---
title: "Covid Stress Data cleaning and Visualization"
subtitle: Project covidistress
Author: "Author: Usama Ashfaq"
output:
  html_document:
    toc: yes
    df_print: paged
  html_notebook:
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---
### Taken from the transparencies of
### COVIDiSTRESS global survey network  (2020, March 30). COVIDiSTRESS global survey. DOI 10.17605/OSF.IO/Z39US, Retrieved from osf.io/z39us

We will load the libraries to carry out the analyses and cleaning of the data.

# Load libraries
```{r, message = FALSE}
library(pacman)

p_load(qualtRics, tidyverse, stringr, multicon, psych)
```

Reading the COVIDSTRESS csv file. Put the file in the same working directory as R studio. This read_survey function from qualtRics keep the header and remove the first two non-data rows

# Load dataset
```{r, message = FALSE, cache=TRUE}

d <- read_survey("COVIDiSTRESS import April 6 2020 (choice values).csv")

```

## Basic information about the completeness of the survey
How many people do not give consent to participate?
We will use only those records for which the user has maked Consent as Yes. Means that they have allowed their given data to be used for scientific research.

```{r}
d %>% 
  filter(Consent == "No") %>% 
  nrow()
```
644 people have marked conscent as "No". We will filter now only those records for which consent is "Yes"

```{r}
#Filter for cases with consent
d <- filter(d, Consent == "Yes")
```

## Survey completetion for those who give consent to the study
How many participants get to the last survey page and have answered every question.

```{r}
sum(d$Finished) / nrow(d)
```
What was the average percentege of completeness in the survey for each individual?

```{r, cache=TRUE}
participant_completeness_rate <- apply(X = d[,11:135], MARGIN = 1, FUN = function(x){
  
  sum(!is.na(x))/length(x)
})

describe(participant_completeness_rate)
```
How many people have answered only one question?

```{r}
length(which(participant_completeness_rate < (2/125)))
```
Out of total 86751 participants only 8068 have answered only one question. 
Lets see What was the averge completeness rate within each question?

```{r}
question_completeness_rate <- apply(X = d[,11:135], MARGIN = 2, FUN = function(x){
  sum(!is.na(x))/length(x)
})

describe(question_completeness_rate)
```
## Visualization of the survey Trend

We will observe that whether our survey trend is similar to other online surveys.

```{r}
library(ggplot2)

#
#qplot(seq_along(question_completeness_rate),question_completeness_rate) + geom_line()

df <- data.frame(seq_along(question_completeness_rate),question_completeness_rate)
ggplot(df,aes(x=seq_along(question_completeness_rate),y=question_completeness_rate))+ geom_line()+ theme_linedraw()+ggtitle("Online survey Trend Visulization") +
  theme(plot.title = element_text(hjust = 0.5))+ theme(plot.title = element_text(face = "bold"))


```
Overall the graph shows similar trend as other online survey.
This plot is very crude but we can spot some certain issues with our survey. The general trend is similar to other online surveys however those strange drops need to be examined furhter. 

1.The first two drops are the experimental questions 
Dem$state: Open end questions. Most of the people choose not to write anything as expected.

AD Gain,AD loss: If Program A is adopted, 200 people will be saved.   
# (half participant got 1 and half got 2). 

2.The 3rd, 4th and 5th are open ended question.
(Expl_Distress_txt)   
(Expl_coping_txt ) 
(Final_open)
Open end questions. Most of the people choose not to write anything as expected.


Let see the number of cases from each country.Brunei needs to be recoded to Bulgaria!

```{r}

d %>% group_by(Country) %>% summarize(n()) %>% print(n=1000)
```

Lets see the number of participants in each language.
```{r}

d %>% group_by(UserLanguage) %>% summarize(n()) %>% print(n=1000)
```

# Data cleaning
Look at the data type. We need to recode character to factor  
```{r}
glimpse(d)
```

## Recode some variables
### Recode education level (self & mom)
We will remove "-" from the following two columns and adjust the response to a certain value to be used later for analysis and visualization.We will group people answering "1" and "None" in the same group
```{r}
d$Dem_edu <- str_remove(d$Dem_edu, "- ")
d$Dem_edu_mom <- str_remove(d$Dem_edu_mom, "- ")


d$Dem_edu <- str_replace(d$Dem_edu, "None|^1", "None/Uninformative response")
d$Dem_edu_mom <- str_replace(d$Dem_edu_mom, "None|^1", "None/Uninformative response")
```

### Recode marital status 
We will recode the martial status becaucse it is inconsistance between different languagas in Qualtrics import. 
Qualtrics is a powerful online survey tool that allows one to build surveys, distribute surveys and analyze responses from one convenient online location!
```{r}

library(dplyr)
recode_if <- function(x, condition, ...) {
  if_else(condition, recode(x, ...), x)
}

# Fix differences in scoring between english and other languages 
d <- d %>%
  mutate(Dem_maritalstatus = 
           recode_if(Dem_maritalstatus, UserLanguage != "EN", 
                     "Single" = "Other or would rather not say",
                     "Married/cohabiting" = "Single",
                     "Divorced/widowed"= "Married/cohabiting",
                     "Other or would rather not say" = "Divorced/widowed"))
```

### Convert character strings to factor

For all demographics variables we will convert the strings to factor.

```{r}
#Demographic information
d[,12:25] <- d[,12:25] %>% 
  mutate_if(is.character, as.factor)
```

```{r}
glimpse(d[, 12:25])
```

### Recode AD_Check, AD_gain and AD_loss

We will recode the the AD_Check, AD_gain and AD_loss to shorten the response and turn the character to factor
```{r}
d <- d %>% 
  mutate(AD_gain = factor(recode(AD_gain, 
                          "路 If Program A is adopted, 200 people will be saved." ="Program A",
                   "路 If Program B is adopted, there is 1/3 probability that 600 people will be saved, and 2/3 probability that no people will be saved" = "Program B")),
         AD_loss = factor(recode(AD_loss, 
                          "路 If Program C is adopted 400 people will die." = "Program C",
                          "路 If Program D is adopted there is 1/3 probability that nobody will die, and 2/3 probability that 600 people will die." = "Program D")),
         AD_check = factor(AD_check))
```


### Convert scale responses to numeric 

We will conver all the responses containg option of "Never", "Almost never","Sometimes", "Fairly often","Very often" to 1,2,3,4,5

```{r}
d <- d %>% mutate_at(
  .vars = vars(contains("PSS10")),
  .funs = recode, 
  "Never" = 1, 
  "Almost never" = 2,
  "Sometimes" = 3, 
  "Fairly often" = 4,
  "Very often" = 5
  )
```

```{r, message = FALSE, echo=FALSE, warning=FALSE}
d <- d %>% mutate_at(
  .vars = vars(matches("Corona_concerns|Compliance|BFF|Distress|SPS|Coping|Expl_media")),
  .funs = recode, 
  "Strongly disagree" = 1, 
  "Disagree" = 2,
  "Slightly disagree" = 3, 
  "Slightly agree" = 4,
  "Agree" = 5,
  "Strongly agree" = 6
)
```
### Recoding Trust_countryrmeasure

We will convert the strings to numeric responses.

```{r}

d <- d %>% mutate(
  Trust_countrymeasure = recode(Trust_countrymeasure,
  "Too little" = 0,
  "1" = 1,
  "2" = 2,
  "3" = 3,
  "4" = 4,
  "Appropriate" = 5,
  "6" = 6,
  "7" = 7,
  "8" = 8,
  "9" = 9,
  "Too much" = 10))
```

## Create composite scores
### PSS10 and Loneliness

```{r}

PSS10set <- d[, grep("PSS10", names(d))]
PSS10list <- list(PSS10_avg = c(1:3, -4, -5, 6, -7, -8, 9, 10),
                  Lon_avg = c(11:13)) 
PSS10score <- scoreTest(PSS10set, PSS10list, nomiss = 0.01, rel = F)
d <- data.frame(d, PSS10score)
```

#### Reliability of the scale
```{r}

alpha(PSS10set[1:10], keys = c("Scale_PSS10_UCLA_4",
                               "Scale_PSS10_UCLA_5",
                               "Scale_PSS10_UCLA_7",
                               "Scale_PSS10_UCLA_8"))
```

```{r}
alpha(PSS10set[11:13])
```

### Compliance
```{r}
Compset <- d[, grep("Compliance", names(d))]
Complist <- list(Compliance_avg = c(1:3, -4, 5, -6)) 

#Not sure if buying large groceries is against the recommendations, I'd say yes?

Compscore <- scoreTest(Compset, Complist, nomiss = 0.01, rel = F)
d <- data.frame(d, Compscore)
```
##### reliability of the scale
```{r}
alpha(Compset, keys = c("Compliance_4",
                        "Compliance_6"))
```

### BFF_15
```{r}
BFF15set <- d[, grep("BFF_15", names(d))]
BFF15list <- list(neu = c(1, 2, -3), 
                  ext = c(4, 5, -6),
                  ope = c(7, 8, 9),
                  agr = c(10, 11, -12),
                  con = c(13, -14, 15)) 
BFF15score <- scoreTest(BFF15set, BFF15list, nomiss = 0.01, rel = F)
d <- data.frame(d, BFF15score)
```

##### reliability of the scale
```{r}
#reliability of the scale
alpha(BFF15set[1:3], keys = "BFF_15_3")
alpha(BFF15set[4:6], keys = "BFF_15_6")
alpha(BFF15set[7:9])
alpha(BFF15set[10:12], keys = "BFF_15_12")
alpha(BFF15set[13:15], keys = "BFF_15_14")
```

### SPS10
```{r}
SPS10set <- d[, grep("SPS", names(d))]
SPS10list <- list(SPS_avg = c(1:3, -4, 5, -6)) 
SPS10score <- scoreTest(SPS10set, SPS10list, nomiss = 0.01, rel = F)
d <- data.frame(d, SPS10score)
```

#### reliability of the scale

```{r}
#reliability of the scale
alpha(SPS10set)
```

### Corona Concern
```{r}
corCset <- d[, grep("Corona_concerns", names(d))]
corClist <- list(corC_avg = c(1:5)) 
corCscore <- scoreTest(corCset, corClist, nomiss = 0.01, rel = F)
d <- data.frame(d, corCscore)
```

##### reliability
```{r}

alpha(corCset)
```

# Data visualization
## Basic information by major countries
We have picked the major countries randomly. You can use glimpse(d$Country) to see all the countrries present in the data set and pick your own country which you want to visualize
```{r}
dsub<-subset(d, Country %in% c("India", "Pakistan", "China", "Germany", "Russia", "Italy","France")) 

#subset countries needed

#load function to calculate means and SD
data_summary <- function(data, varname, groupnames){
  require(plyr)
  summary_func <- function(x, col){
    c(mean = mean(x[[col]], na.rm=TRUE),
      sd = sd(x[[col]], na.rm=TRUE))
  }
  data_sum<-ddply(data, groupnames, .fun=summary_func,
                  varname)
  data_sum <- rename(data_sum, c("mean" = varname))
  return(data_sum)
}

#create dataframe for the plot
df_bar<- data_summary(dsub, varname="PSS10_avg", 
                    groupnames="Country")

head(df_bar) #check the stats
```

### plot with basic layout. Customize at will
```{r}
library(ggplot2)
ggplot(df_bar, aes(x=fct_reorder(Country, PSS10_avg), y=PSS10_avg, width=.6,fill=Country))+
  geom_bar(stat="identity",position=position_dodge()) +
  geom_errorbar(aes(ymin=PSS10_avg-sd, ymax=PSS10_avg+sd), width=.2, #to obtain also the lower part of the SD bar use <ymin=PSS10_avg-sd>
                 position=position_dodge(.9))+
  ggtitle("Stress Levels of different countries")+
  theme(plot.title = element_text(hjust = 0.5))+
  theme_bw()+theme(panel.grid = element_blank(), 
        legend.position = "none")+
  xlab("Country")+
  ylab("Stress Level")+
  ylim(0,5)+ theme(axis.text.x = element_text(face = "bold"))+ theme(legend.position = "none") +theme(plot.title = element_text(hjust = 0.5))
```

Here we can see that Pakistan and India has highest Stress level due to France and Italy has the lowest Stress level from the countries we have selected. The upper and lower line represents upper and lower link and middle line represents the average value of stress for the respective countries.

### Visualization of the distress scale
```{r}
d %>% summarize_at(.vars = dplyr::vars(matches("Distress_\\d")), .funs = mean, na.rm= T) %>% 
  pivot_longer(cols = everything(), names_to = "Source", values_to = "Value") %>% 
  mutate(Source = dplyr::recode(Source,
         "Expl_Distress_1"="Income",
         "Expl_Distress_2"="Work",
         "Expl_Distress_3"="Children's education",
         "Expl_Distress_4"="Job prospects",
         "Expl_Distress_5"="Access to necessities (food etc.)",
         "Expl_Distress_6"="No social activities",
         "Expl_Distress_7"="No religious activities",
         "Expl_Distress_8"="Behavior of adults I live with",
         "Expl_Distress_9"="Behavior of children I live with",
         "Expl_Distress_10"="National economy",
         "Expl_Distress_11"="Civil services (police, sanitation...)",
         "Expl_Distress_12"="Risk of catching coronavirus",
         "Expl_Distress_13"="Risk of being hospitalized or dying",
         "Expl_Distress_14"="Worry over friends and relatives who live far away",
         "Expl_Distress_15"="Adapt work to digital platforms",
         "Expl_Distress_16"="Adapt to social life on digital platforms",
         "Expl_Distress_17"="Feeling ashamed for acting differently",
         "Expl_Distress_18"="Loneliness",
         "Expl_Distress_19"="Time I spend inside",
         "Expl_Distress_20"="Time I spend in proximity to others",
         "Expl_Distress_21"="Not knowing about developments with COVID",
         "Expl_Distress_22"="Not knowing how to stop COVID",
         "Expl_Distress_23"="Not knowing how long the measures will last",
         "Expl_Distress_24"="No travel outside my country")
  ) %>% 
  ggplot(aes(x = fct_reorder(Source, Value), y = Value)) + 
  geom_bar(stat = "identity", position = position_dodge(), color="black", fill="green",)+scale_y_continuous(breaks = seq(1,8,1))+
  coord_flip(ylim = c(1,5))+
  theme_bw()+
  xlab("Source of distress")+
  ylab("Level of distress")+  theme(axis.text.y = element_text(face = "bold"))+  ggtitle("Sources of Distress during Corona")+theme(plot.title = element_text(hjust = -0.5))
```

The above bar plot shows the level of stress for different sources. People are more stressed due to the fear of economy collapse and catching corona virus but having no religious activities have causes least stress to the people.

### Visualization of the coping scale
```{r}
d %>% summarize_at(.vars = dplyr::vars(matches("Coping_\\d")), .funs = mean, na.rm= T) %>% 
  pivot_longer(cols = everything(), names_to = "Source", values_to = "Value") %>% 
  mutate(Source = dplyr::recode(Source,
                                "Expl_Coping_1"="Information from the government",
                                "Expl_Coping_2"="Face-to-face interactions friends/family",
                                "Expl_Coping_3"="Phonecalls/long-range interactions friends/family",
                                "Expl_Coping_4"="Face-to-face interactions colleagues",
                                "Expl_Coping_5"="Phonecalls/long-range interactions colleagues",
                                "Expl_Coping_6"="Social media",
                                "Expl_Coping_7"="Video games (alone)",
                                "Expl_Coping_8"="Video games (online)",
                                "Expl_Coping_9"="Watching TV-shows or movies",
                                "Expl_Coping_10"="Helping others",
                                "Expl_Coping_11"="Preparing for the crisis",
                                "Expl_Coping_12"="Following government's advice",
                                "Expl_Coping_13"="My work/vocation",
                                "Expl_Coping_14"="Hobby",
                                "Expl_Coping_15"="God or Religion",
                                "Expl_Coping_16"="Knowledge of actions take by government or civil service")) %>% 
  ggplot(aes(x = fct_reorder(Source, Value), y = Value)) + 
  geom_bar(stat = "identity", position = position_dodge(), color="black", fill="lightblue")+
  coord_flip(ylim = c(1,5))+
  theme_bw()+
  xlab("Source of coping")+
  ylab("Level of coping") + theme(axis.text.y = element_text(face = "bold")) + ggtitle("How people usually cope with \nCorona Stress")
```

The above boxplot represents which methods people are using to cope with the Corona stress. According to this survey, people prefer the long range interaction with family and friends and spend time doing some hobby to cope with the Corona stress.

### Visualization of trust
```{r}
d %>% summarize_at(.vars = dplyr::vars(matches("OECD")), .funs = mean, na.rm= T) %>% 
  pivot_longer(cols = everything(), names_to = "Source", values_to = "Value") %>% 
  mutate(Source = dplyr::recode(Source,
                                "OECD_people_1"="Majority of people",
                                "OECD_people_2"="Majority of people I know personally",
                                "OECD_insititutions_1"="Country's Parliament/government",
                                "OECD_insititutions_2"="Country's Police",
                                "OECD_insititutions_3"="Country's Civil service",
                                "OECD_insititutions_4"="Country's Healthcare system",
                                "OECD_insititutions_5"="WHO",
                                "OECD_insititutions_6"="Government's measures against COVID")) %>% 
  ggplot(aes(x = fct_reorder(Source, Value), y = Value)) + 
  geom_bar(stat = "identity", position = position_dodge(), color="black", fill="darkred")+
  coord_flip(ylim = c(1,10))+
  scale_y_continuous(breaks = seq(1,10,1))+
  theme_bw()+
  xlab("Source")+
  ylab("Level of trust")+ theme(axis.text.y = element_text(face = "bold")) + ggtitle("Trust level on different information sources")
```

The above bar plot represents people trust on different sources on information. Clearly the people trust the information coming from those people they know and WHO. 


### Visualization of concern
```{r}
d %>% summarize_at(.vars = dplyr::vars(matches("concern")), .funs = mean, na.rm= T) %>% 
  pivot_longer(cols = everything(), names_to = "Source", values_to = "Value") %>% 
  mutate(Source = dplyr::recode(Source,
                                "Corona_concerns_1"="... me personally",
                                "Corona_concerns_2"="... my family",
                                "Corona_concerns_3"="... my close friends",
                                "Corona_concerns_4"="... my country",
                                "Corona_concerns_5"="... other countries")) %>% 
  ggplot(aes(x = fct_reorder(Source, Value), y = Value)) + 
  geom_bar(stat = "identity", position = position_dodge(), color="black", fill="yellow")+
  coord_flip(ylim = c(1,6))+
  scale_y_continuous(breaks = seq(1,6,1))+
  theme_bw()+
  xlab("I worry for...")+
  ylab("Level of worry")+ theme(axis.text.y = element_text(face = "bold")) + ggtitle("People worry the most about")
```
This bar plot shows that the people worry most about their family and their country during the corona pandemie. Here an interesting finding is that the people care the least about themselves.

### Visualization of compliance
```{r}
d %>% summarize_at(.vars = dplyr::vars(matches("Compliance_\\d")), .funs = mean, na.rm= T) %>% 
  pivot_longer(cols = everything(), names_to = "Source", values_to = "Value") %>% 
  mutate(Source = dplyr::recode(Source,
                                "Compliance_1"="I am well informed how I can stop\nthe spread of coronavirus",
                                "Compliance_2"="I have done everything to reduce\nthe spread of coronavirus",
                                "Compliance_3"="I have done everything to stop keep\nthe phyisical distance",
                                "Compliance_4"="I feel that keeping distance\nwould have a high personal cost",
                                "Compliance_5"="I trust others follow guidelines\nto stop the spread of coronavirus",
                                "Compliance_6"="I have bought large extra supplies")) %>% 
  ggplot(aes(x = fct_reorder(Source, Value), y = Value)) + 
  geom_bar(stat = "identity", position = position_dodge(), color="black", fill="blue")+
  coord_flip(ylim = c(1,6))+
  scale_y_continuous(breaks = seq(1,6,1))+
  theme_bw()+
  xlab("Compliance")+
  ylab("Level of agreement") + theme(axis.text.y = element_text(face = "bold")) + ggtitle("Compliance/Obiedience of instructions to prevent \ns pread of Corona Virus ")
```

The above box plot represent that to which level the people are following the general health and other instructions given to them by the different organisation and their countries. This data can be biased also since people will tend to avoid leaving a negative impression

### Visualization of media
```{r}
d %>% summarize_at(.vars = dplyr::vars(matches("media_\\d")), .funs = mean, na.rm= T) %>% 
  pivot_longer(cols = everything(), names_to = "Source", values_to = "Value") %>% 
  mutate(Source = dplyr::recode(Source,
                                "Expl_media_1"="... the government",
                                "Expl_media_2"="... independent news outlets in the coutnry",
                                "Expl_media_3"="... news outlets outside the country",
                                "Expl_media_4"="... friends and family",
                                "Expl_media_5"="... social media",
                                "Expl_media_6"="I have heard more positive than negative\nstories about people's behavior")) %>% 
  ggplot(aes(x = fct_reorder(Source, Value), y = Value)) + 
  geom_bar(stat = "identity", position = position_dodge(), color="black", fill="darkred")+
  coord_flip(ylim = c(1,6))+
  scale_y_continuous(breaks = seq(1,6,1))+
  theme_bw()+
  xlab("I have sought information from...")+
  ylab("Level of agreement") + theme(text = element_text(size = 12))  + theme(axis.text.y = element_text(face = "bold")) + ggtitle("Level of agreement on different \ninformation resources")
```
The box plot shows the people trust or level of agreement regarding different information sources. The people look the most for information regarding corona from the country and the independent news outlet in the country.

### Bivariate plots of relevant scales
#### Basic summary statistics
```{r}
#Understand
Hmisc::describe(d[, 136:145])
```

#### Bivariate plots to visualize the relationship between Perceived Stress, Social Support, Loneliness, and extraversion, colored by gender
```{r, fig.width = 12, fig.height = 12}
#Understand
library(GGally)

d1 <- d %>% 
  select(PSS10_avg, Lon_avg, SPS_avg, ext, Dem_gender)%>% filter(Dem_gender=="Male" | Dem_gender=="Female")

levels(d1$Dem_gender)[levels(d1$Dem_gender) == "Other/would rather not say"] = "Undisclosed"

#d1$Dem_gender <- addNA(d1$Dem_gender)

p <- ggpairs(d1, columnLabels = c("Perceived Stress", "Loneliness", "Perceived Support", "Extraversion", "Gender"),
             mapping = ggplot2::aes(col = Dem_gender, alpha = .2),
             upper = list(continuous = wrap("cor", size = 3)),
             title = "Bivariate relationship of Perceived Stress, Social Support, Loneliness, and Extraversion")+ theme(title = element_text(face = "bold"))+theme(plot.title = element_text(hjust = 0.5))+theme(text = element_text(size = 14))

print(p, progress = FALSE)
```
The above matrix of plots shows the bivariate relationships of Gender, Extroversion, Precieved Support, Precieved Stress, Loneliness among male and Females.
1. Lonliness tends to increase Precieved Stress
2. Preceived reduces the Precieved Stress
3. Extraversion (Socilizing/Extravert) reduces the Precieved Stress

####Bivariate plots to visualize the relationship between Perceived Stress, Social Support, Loneliness, and extraversion 
```{r, fig.height = 12, fig.width = 12}
#Understand
p1 <- ggpairs(d1, columns = 1:4,
             columnLabels = c("Perceived Stress", "Loneliness", "Perceived Support", "Extraversion"),
             upper = list(continuous = wrap("cor", size = 3, colour = "Blue")),
             lower=list(continuous=wrap("smooth", colour="Red")),
             title = "Bivariate relationship of Perceived Stress, Social Support, Loneliness, and Extraversion") + theme(title = element_text(face = "bold"))+theme(plot.title = element_text(hjust = 0.5))+theme(text = element_text(size = 14))

print(p1, progress = FALSE)
```
The above matrix of plots shows the bivariate relationships of Gender, Extraversion, Precieved Support, Precieved Stress, Loneliness. The findings are similar as explained above just a different visulization.
```{r}
write.csv(d, file = "clean_world.csv")
```


