---
title: "Twitter Analysis"
author: "Vishnu Jayanand"
date: "June 19th, 2021"
output:
  html_document:
    css: style.css
    df_print: paged
    toc: true
    number_sections : true
    toc_depth: 2
    toc_float: true 
    theme: flatly
    highlight: textmate
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# **Overview** {-} 

We propose to know the impact of COVID-19 tackling infodemics and misinformation on
Twitter. This is done by extracting recent popular tweets from a specific location across different countries.
It will help us describe the false information that is spread with the sole purpose of causing confusion and
harm. We target to extract hashtags like #covid19, #misinformation, #fakenews, #disinformation, #, etc.,
to get the related posts about it and analyze how the information processing and decision-making behaviors
are compromised. We perform sentimental analysis on the tweets to understand the sentiments of people
which is crucial during the time of this pandemic

# Twitter Data

We have primarily two datasets - one of them contains tweets from the onset of the pandemic and the other are very recent tweets (June 2021). Our main objective here is to figure out 
how the sentiments have changed over the months.

For the security purposes, we show the skeletal code to extract the tweets using fake credentials. We would load the data via .rds file for our extracted tweets.

```{r connection, eval=FALSE}
library(rtweet)
library(dplyr)
library(tidyr)
library(twitteR)
library(tidytext)

appname <- "CovidDistress"
key <- "ogRXvxribQAEt9tJKQ1rEd0c0"
secret <- "HlvVRoFg73JJcpcGjYxUWBagWratEIrdagPCeaiToWTKa15vCO"
access_token <- "15914217-8YYyRRAxRBL0Vu9Y0tAjVFfPvdJdYByfmsiVpLEoD"
access_secret <- "oeXIkYHBTQpGRxZCKI4q67UN3L8PuJfwb0su6EOkIk22f" 

twitter_token <- create_token(
  app = appname,
  consumer_key = key,
  consumer_secret = secret,
  access_token = access_token,
  access_secret = access_secret,
  set_renv = TRUE)

corona_tweets <- search_tweets(q = "#covid19 OR #coronavirus", n=20000, include_rts=FALSE, lang="en", retryonratelimit = TRUE)

saveRDS(corona_tweets, "../data/tweets2021.rds")
```

We can now load saved RDS file using the command below
```{r loadRDS}
tweets2021_raw <- readRDS("../data/tweets2021.rds")

```

There are `r nrow(tweets2021_raw)` tweets from the dataset which is more than what we intended. This is because we set **retryonratelimit** to TRUE. These tweets are dated from ***`r format(as.Date(min(tweets2021_raw$created_at)), "%B %d %Y")`*** to ***`r format(as.Date(max(tweets2021_raw$created_at)), "%B %d, %Y")`***

Here's a sample row from the dataset
```{r echo=FALSE}
gt::gt(tweets2021_raw[1,])
```